Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
Remove redundant parentheses

\begin{quote}\small\begin{verbatim}
launchMissiles >>=
  (`shouldBe` (Left "not implemented"))
\end{verbatim}\end{quote}

@@

\begin{quote}\small\begin{verbatim}
launchMissiles `shouldReturn` (Left "not implemented")
\end{verbatim}\end{quote}

@@

\begin{quote}
\emph{kazu: are parentheses necessary? how about following?}
\begin{verbatim}
  launchMissiles >>=
  (`shouldBe` Left "not implemented")
  launchMissiles `shouldReturn` Left "not implemented"
\end{verbatim}
\end{quote}

>>>>

\begin{quote}\small\begin{verbatim}
launchMissiles >>=
  (`shouldBe` Left "not implemented")
\end{verbatim}\end{quote}

@@

\begin{quote}\small\begin{verbatim}
launchMissiles `shouldReturn` Left "not implemented"
\end{verbatim}\end{quote}

@@
